TODO: A Survey of StarCraft AI Techniques

### 2012-02-26 survey.tex
added some biblio on opponent modeling

\begin{itemize}
\item Task Decomposition (or ``Architecture'')
\item Integration of Domain Knowledge
\item Reasoning with Uncertainty (including information gathering)
\item Opponent Modeling and Adaptation
\item Group and Individual Control (``micro'')
\item Planning and Resource Allocation (``macro'')
\item Spatial reasoning (``tactics'')
\end{itemize}

@@

>>>>

\begin{itemize}
\item Task Decomposition (or ``Architecture'')
\item Integration of Domain Knowledge
\item Reasoning with Uncertainty (including information gathering)
\item Opponent Modeling and Adaptation: opponent modeling is key if we have to adapt our strategy. As different strategies are dominating each others, forming multiple Nash equilibria, the AI has to be able to infer the intend of its opponent.
\item Group and Individual Control (``micro''): the task of controlling units efficiently (we can not speak of optimality here due to the huge state space, and of the enemy behavior entails numerous Nash equilibria), focusing fire to diminish enemy's firepower and keeping our units alive the longest, casting defensive and offensive spells and abilities.
\item Planning and Resource Allocation (``macro'')
\item Spatial reasoning (``tactics'')
\end{itemize}

@@

\subsection{Opponent modeling, strategy prediction}

There are related works in the domains of opponent modeling \cite{HsiehS08,SchaddBS07,OBRecog}. The main methods used to these ends are case-based reasoning (CBR) and planning or plan recognition \cite{LTW,CBR_Planning,OntanonCBR,HTNPlanning,Ramirez}. There are precedent works of Bayesian plan recognition \cite{BMPR}, even in games with Albrecht \textit{et al.} \cite{BayesianRecog} using dynamic Bayesian networks to recognize a user's plan in a multi-player dungeon adventure.

\cite{LTW} used CBR to perform dynamic plan retrieval extracted from domain knowledge in Wargus (Warcraft II clone). \cite{CBR_Planning} base their real-time case-based planning (CBP) system on a plan dependency graph which is learned from human demonstration. In \cite{OntanonCBR,PlanRetrieval}, they use CBR and expert demonstrations on Wargus. They update their previous CPB approach by using ``situation assessment'' for plan retrieval. They improve the speed of CPB by using a decision tree to select relevant features. Hsieh and Sun \cite{HsiehS08} based their work on \cite{LTW} CBR model and used StarCraft replays to construct states and building sequences. Strategies are choices of building construction order in their model.

\cite{SchaddBS07} describe opponent modeling through hierarchically structured models of the opponent behaviour and they applied their work to the Spring RTS (Total Annihilation clone). \cite{HTNPlanning} use hierarchical task networks (HTN) to model strategies in a first person shooter with the goal to use HTN planners. \cite{OBRecog} improve the probabilistic hostile agent task tracker (PHATT \cite{PHATT}, a simulated HMM for plan recognition) by encoding strategies as HTN. %\cite{Madeira06} 
\cite{WeberCig09} proposed ``a data mining approach to strategy prediction'' and performed supervised learning on StarCraft replays. \cite{HMMstrat_RTS_AIIDE11} used HMM to learn the transition probabilities of sequences of constructions and kept the most probables to produce probabilistic behavior models (in StarCraft). \cite{SynnaeveOpeningCig11} continued on \cite{WeberCig09} and used a Bayesian semi-supervised (labeling based on clustering) model to learn from replays and predict openings (early game strategies) from StarCraft replays, while \cite{SynnaeveAIIDE11} presents a whole game Bayesian tech-tree predictor based on unserpervised learning from replays.
